%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip}
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[style=authoryear,sorting=ynt,maxbibnames=2]{biblatex}
\usepackage[unicode,draft=false]{hyperref}
\usepackage{fontawesome5}
\usepackage{array}

\newcolumntype{C}{>{\centering\arraybackslash}X}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{
  colorlinks,
  breaklinks,
  urlcolor=linkcolour,
  linkcolor=linkcolour
}

\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

\newenvironment{jobshort}[2]
{
  \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill & #2 \\[3.75pt]
  \end{tabularx}
}
{
}

\newenvironment{joblong}[2]
{
  \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill & #2 \\[3.75pt]
  \end{tabularx}
  \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut,leftmargin=1em,itemsep=3pt,label=--]
}
{
    \end{itemize}
  \end{minipage}
}

\begin{document}

\pagestyle{empty}

%----------------------------------------------------------------------------------------
% TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{}C@{}}
  \Huge{Ellen Poulsen} \\[7.5pt]
  \href{https://linkedin.com/in/ellenpoulsen07}{\raisebox{-0.05\height}\faLinkedin\ Ellen Poulsen}
  \ $|$\ 
  \href{mailto:ecpoulse@calpoly.edu}{\raisebox{-0.05\height}\faEnvelope\ ecpoulse@calpoly.edu}
  \ $|$\ 
  \href{tel:+15416542129}{\raisebox{-0.05\height}\faMobile\ +1 (541) 654-2129} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{tabularx}{\linewidth}{@{}l X@{}}
  2025--Present
  & B.S. Aerospace Engineering \hfill \normalsize (GPA: 3.751/4.0) \\
  & \textbf{California Polytechnic State University, San Luis Obispo} \\

  2021--2025
  & Sheldon High School, Eugene OR \hfill (GPA: 3.98/4.00) \\
  & International Baccalaureate Diploma Programme Graduate \\

  2023
  & Recipient of the Oregon State Seal of Biliteracy in Spanish \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{tabularx}{\linewidth}{@{}l r@{}}
  \textbf{Sheldon Astronomy Club --- Construction of Dobsonian Telescope}
  & \hfill \href{https://drive.google.com/file/d/157D7coOipqPLUvzPUul57gm_RRA5Iq2_/view?usp=sharing}{Link to Article} \\

  \multicolumn{2}{@{}X@{}}{
    Co-founded and acted as co-presdient of Sheldon Astronomy Club for four years: organizing weekly presentations on astrophysics, observational astronomy, and space news. Expanded partnership with the Eugene Astronomical Society (EAS), securing equipment and textbook donations. Led construction of an 8-inch Dobsonian telescope in partnership with the EAS, giving members hands-on experience in applied mathematics and design. The telescope was featured in the August 2025 edition of \textit{Sky \& Telescope}.
  } \\[6pt]
\textbf{Cal Poly Space Systems --- Liquids Project} & \\
  \multicolumn{2}{@{}X@{}}{
    Team member developing a bipropellant liquid rocket engine and test stand, with the goal of full rocket integration. Embracing Cal Poly's "Learn by Doing" approach, we contribute to development of propulsion, controls, and testing.
  } \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% LEADERSHIP EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Leadership Experience}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Sheldon High School Associated Student Body (ASB)} & \hfill\\
\multicolumn{2}{@{}X@{}}{
Serving on the Sheldon High School Associated Student Body was a defining part of my high school experience, allowing me to develop the strong leadership skills I have today. My experience culminated in serving as ASB Executive President, where I oversaw and led all other branches of leadership and more than 80 students. This included school fundraisers, events, and assemblies, while also acting as a student-admin liaison advocating on behalf of my peers and faculty. This experience showed me how to stand up for issues I believe in, communicate effectively, and work collaboratively alongside others.
} \\[6pt]
\textbf{Society of Women Engineers at Cal Poly} & \hfill \\
\multicolumn{2}{@{}X@{}}{
The Society of Women Engineers offers professional development opportunities and connections with industry professionals, while members work to advocate for and support women underrepresented in their fields. Joining the Spring Elementary Engineering Day subcommittee has given me the opportunity to advance access to education in my community and inspire the next generation of girls in engineering and technology.
}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Work Experience}

\begin{jobshort}{Freelance Photography}{2023--Present}
Experience working in professional photography, including for notable organizations such as the Eugene Marathon, Eugene Ballet Company, and Insta Ballet. I worked to plan, direct, and process photos for social media, magazines, and programs. I also managed individual freelance photoshoots, volunteered my photography for school sports and events, and explored astrophotography. These opportunities have given me confidence in my communication skills and allowed me to connect with my community through my artistic vision.
\end{jobshort}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}